---
title: "data_processing_pipeline"
output: html_document
---

# Pipeline 

In this file functional pipeline: raw, but split data into processed data 

Variable-wise steps: 
1. split the data points with multiple values in one categories into multiple rows (done in a python script prior)
2. standardise  

Next steps: 

4. Manual fixes
5. Regex separation of years from authors and other persons is done in another python file 



```{r setup}
library(dplyr)
library(stringr)

data <- read.csv("data/exploded_data.csv")
new_names <- read.csv('data/translated_names.csv')

data_eng <- data
colnames(data_eng) <- new_names$x
```

# translation of variable names 

```{r}
# created with the help of ChatGPT
oop_count <- 0

count_diff_vec <- function(before, after) {
  sum((before != after) | (is.na(before) != is.na(after)), na.rm = TRUE)
}

count_diff_df <- function(before, after) {
  # If dimensions differ, count:
  # 1. all new rows as changes
  # 2. plus cell-wise diffs on overlapping part
  
  min_rows <- min(nrow(before), nrow(after))
  min_cols <- min(ncol(before), ncol(after))
  
  # compare overlapping part
  overlap_before <- before[seq_len(min_rows), seq_len(min_cols), drop = FALSE]
  overlap_after  <- after[seq_len(min_rows), seq_len(min_cols), drop = FALSE]
  
  cell_diffs <- sum(
    (overlap_before != overlap_after) |
    (is.na(overlap_before) != is.na(overlap_after)),
    na.rm = TRUE
  )
  
  # count extra cells from row/column expansion
  extra_cells <- abs(nrow(after) * ncol(after) - min_rows * min_cols)
  
  return(cell_diffs + extra_cells)
}

track_vec <- function(vec, fn) {
  before <- vec
  after <- fn(vec)
  op_count <<- op_count + count_diff_vec(before, after)
  return(after)
}

track_df <- function(df, fn) {
  before <- df
  after <- fn(df)
  op_count <<- op_count + count_diff_df(before, after)
  return(after)
}
```


```{r, eval=F}
# translated names 

translated_names <- c(
  'teaviku_laad'="publication_type",
  'sihtrühm'="target_audience", 
  'pealkiri'="title",
  'autor'="author",
  'originaal_pealkiri'="title_original",
  'Žanr'="genre",
  'tõlkija'="translator", 
  'lähtekeel'="source_language", 
  'lähtekirjandus'="source_literature",
  'toimetaja'="editor",
  'ees__järelsõna_autor'="fore_afterword_author",
  'ilmumiskoht'="publication_location",
  'kirjastaja'="publisher", 
  'ilmumisaasta'="publication_year", 
  'füüsiline_kirjeldus'="physical_description", 
  'trükikordus'="edition", 
  'sarjaandmed'="series", 
  'arvustatava_tõlkeraamatu_autor'="author_of_translated_book_under_review_to_be_removed", 
  'väljaanne'="issue", 
  'number_leheküljed'="n_pages", 
  'sisu'="content", 
  'märkused'="notes", 
  'id'="id") 

write.csv(translated_names, 'data/translated_names.csv')
```



# Standardisation of the variables 



## `publishing_year`

Split years from 19181919 -> 1918 and 1919 separate rows 

```{r}
before <- data_eng

A <- data_eng |> filter(str_length(as.character(publication_year))==8) |> 
  mutate(publication_year = str_sub(publication_year, 1, 4))
B <- data_eng |> filter(str_length(as.character(publication_year))==8) |> 
  mutate(publication_year = str_sub(publication_year, 5, 8))
C <- data_eng |> filter(str_length(as.character(publication_year))==12) |> 
  mutate(publication_year = str_sub(publication_year, 1, 4))
D <- data_eng |> filter(str_length(as.character(publication_year))==12) |> 
  mutate(publication_year = str_sub(publication_year, 5, 8))
E <- data_eng |> filter(str_length(as.character(publication_year))==12) |> 
  mutate(publication_year = str_sub(publication_year, 9, 12))

data_eng <- data_eng |> 
  filter(!str_length(as.character(publication_year))%in% c(8,12)) |> 
  rbind(A) |> rbind(B) |> rbind(C) |> rbind(D) |> rbind(E) 

op_count <- op_count + count_diff_df(before, data_eng)

rm(A,B,C,D,E)
```

## `publication_type` 

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.

```{r}
before <- data_eng$publication_type
A <- data_eng |> filter(str_detect(publication_type,', ')) |> 
  mutate(publication_type = str_split_i(publication_type, ', ', i=1))
B <- data_eng |> filter(str_detect(publication_type,', ')) |> 
  mutate(publication_type = str_split_i(publication_type, ', ', i=2))

data_eng <- data_eng |> filter(!str_detect(publication_type,', ')) |> rbind(A) |> rbind(B) 

data_eng <- data_eng |> mutate(publication_type = case_when(
  publication_type %in% c("", " ", "-")  ~ NA,
  publication_type == "Tõlkeraamnat" ~ "Tõlkeraamat", 
  publication_type == "tõlkeraamat" ~ "Tõlkeraamat",
  T ~ publication_type 
)) 

op_count <- op_count + count_diff_vec(before, data_eng$publication_type)

rm(A,B)
```

## `target_audience` 

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.

```{r}
before <- data_eng$target_audience

A <- data_eng |> filter(str_detect(target_audience,', ')) |> 
  mutate(target_audience = str_split_i(target_audience, ', ', i=1))
B <- data_eng |> filter(str_detect(target_audience,', ')) |> 
  mutate(target_audience = str_split_i(target_audience, ', ', i=2))

data_eng <- data_eng |> filter(!str_detect(target_audience,', ')) |> rbind(A) |> rbind(B) 

data_eng <- data_eng |> mutate(target_audience = case_when(
  target_audience %in% c(" ", "") ~ NA, 
  target_audience == "laste- ja noortekirjandus" ~ "Laste- ja noortekirjandus", 
  target_audience == "Täiskasvanute iluirjandus" ~ "Täiskasvanute ilukirjandus", 
  target_audience == "Täiskasvanute lukirjandus" ~ "Täiskasvanute ilukirjandus", 
  target_audience == "Laste ja noortekirjandus" ~ "Laste- ja noortekirjandus", 
  T ~ target_audience
))

op_count <- op_count + count_diff_vec(before, data_eng$target_audience)

rm(A,B)
```

## `genre`

Standardizing:
- split values from "; "
- empty values "" standardize to NULL
- put genres in all lowercase (after filtering out `Muzl, der gestiefelte Kater`)
- all values are in plural 

```{r}

before <- data_eng$genre

A <- data_eng |> filter(str_detect(genre,', ')) |> 
  mutate(genre = str_split_i(genre, ', ', i=1))
B <- data_eng |> filter(str_detect(genre,', ')) |> 
  mutate(genre = str_split_i(genre, ', ', i=2))

data_eng <- data_eng |> filter(!str_detect(genre,', ')) |> rbind(A) |> rbind(B) 

data_eng <- data_eng |> mutate(genre = case_when(
  genre %in% c(" ", "", 'j', "Muzl", "der gestiefelte Kater") ~ NA, 
  genre == "romaanidq" ~ "romaanid",
  genre == "Muzl, der gestiefelte Kater" ~ NA, 
  genre == "romaan" ~ "romaanid", 
  genre == "rtomaanid" ~ "rommanid",
  genre == "dramatiseering" ~ "dramatiseeringud", 
  genre == "jutt" ~ "jutud", 
  genre == "jutus" ~ "jutud", 
  genre == "jutustus" ~ "jutustused", 
  genre == "jutustuse" ~ "jutustused", 
  genre == "jutustusedd" ~ "jutustused", 
  genre == "näidenid" ~ "näidendid", 
  genre == "nälestused" ~ "mälestused", 
  T ~ tolower(genre)
))

op_count <- op_count + count_diff_vec(before, data_eng$genre)

rm(A,B)
```



## `source_language` and `source_literature`

Columns "lähtekeel" and "lähtekirjandus" ()
Standardizing:
- split values from "; "
- empty values "" standardize to NA 
- hyphen '-' (dash) after every vana

```{r} 
before <- data_eng$source_language

#count the hyphens, divide and conquer
A <- data_eng |> filter(str_count(source_language, ", ")==1) |> 
  mutate(source_language = str_split_i(source_language, ', ', i=1))
B <- data_eng |> filter(str_count(source_language, ", ")==1) |> 
  mutate(source_language = str_split_i(source_language, ', ', i=2))

C <- data_eng |> filter(str_count(source_language, ", ")==2) |> 
  mutate(source_language = str_split_i(source_language, ', ', i=1))
D <- data_eng |> filter(str_count(source_language, ", ")==2) |> 
  mutate(source_language = str_split_i(source_language, ', ', i=2))
E <- data_eng |> filter(str_count(source_language, ", ")==2) |> 
  mutate(source_language = str_split_i(source_language, ', ', i=3))

data_eng <- data_eng |> filter(str_count(source_language, ", ")==0) |> 
  rbind(A) |> rbind(B) |> rbind(C) |> rbind(D) |> rbind(E) 
op_count <- op_count + count_diff_vec(before, data_eng$source_language)

rm(A,B,C,D,E)
```


```{r} 
before <- data_eng$source_language

data_eng <- data_eng |> mutate(source_language = case_when(
  source_language %in% c(" ", "", "teadmata", "tedamata", 
                         "teadmata/undetermined") ~ NA,
  source_language %in% c("prantuse", "prantsuse?", "prantsusre")~ "prantsuse", 
  source_language == "sakas" ~ "saksa", 
  source_language == "horvaatia" ~ "horvaadi",
  source_language == "jidiši" ~ "jidiš",
  source_language == "rooitsi" ~ "rootsi",
  source_language == "turkmeeni" ~ "türkmeeni", 
  source_language == "dargiini" ~ "dargi",
  source_language %in% c("vana-usbeki", "vanausbeki") ~ "tšagatai",
  str_detect(source_language, "vana") &
    !str_detect(source_language, "vana-") ~ str_replace(source_language, "vana", "vana-"),
  T ~ tolower(source_language)
)) 

op_count <- op_count + count_diff_vec(before, data_eng$source_language)

```

```{r}
before <- data_eng$source_literature

A <- data_eng |> filter(str_count(source_literature, ", ")==1) |> 
  mutate(source_literature = str_split_i(source_literature, ', ', i=1))
B <- data_eng |> filter(str_count(source_literature, ", ")==1) |> 
  mutate(source_literature = str_split_i(source_literature, ', ', i=2))

C <- data_eng |> filter(str_count(source_literature, ", ")==3) |> 
  mutate(source_literature = str_split_i(source_literature, ', ', i=1))
D <- data_eng |> filter(str_count(source_literature, ", ")==3) |> 
  mutate(source_literature = str_split_i(source_literature, ', ', i=2))
E <- data_eng |> filter(str_count(source_literature, ", ")==3) |> 
  mutate(source_literature = str_split_i(source_literature, ', ', i=3))
G <- data_eng |> filter(str_count(source_literature, ", ")==3) |> 
  mutate(source_literature = str_split_i(source_literature, ', ', i=3))

data_eng <- data_eng |> filter(str_count(source_literature, ", ")==0) |> 
  rbind(A) |> rbind(B) |> rbind(C) |> rbind(D) |> rbind(E) |> rbind(G)  

op_count <- op_count + count_diff_vec(before, data_eng$source_literature)
rm(A,B,C,D,E,G)
```


```{r}
before <- data_eng$source_literature

data_eng <- data_eng |> mutate(source_literature = case_when(
  source_literature %in% c(" ", "", "teadmata", "tedamata",
                           "teadmata/undetermined") ~ NA,
  source_literature %in% c("prantuse", "prantsuse?")~ "prantsuse", 
  source_literature == "sakas" ~ "saksa", 
  source_literature == "horvaatia" ~ "horvaadi",
  source_literature == "jidiši" ~ "jidiš",
  source_literature == "rooitsi" ~ "rootsi",
  source_literature == "turkmeeni" ~ "türkmeeni", 
  source_literature == "dargiini" ~ "dargi",
  source_literature %in% c("vana-usbeki", "vanausbeki") ~ "tšagatai",
  source_literature == "moldaavia" ~ "moldova", 
  source_literature == "moldaavi" ~ " moldova", 
  source_literature %in% c("argeniina","argentiina")~ "argetina", 
  source_literature == "inglised" ~ "inglise", 
  source_literature == "kabardiini" ~ "kabardi", 
  source_literature == "aserbaidžaan" ~ "aserbaidžaani", 
  source_literature =="kolumbia" ~ "colombia", 
  source_literature =="uksraina" ~ "ukraina", 
  source_literature =="uruguai" ~ "uruguay", 
  source_literature =="välis-eesti" ~ "väliseesti", 
  source_literature =="vene'" ~ "vene", 
  source_literature =="venetsueela" ~ "venezuela", 
  str_detect(source_literature, "vana") & 
    !str_detect(source_literature, "vana-") ~ str_replace(source_literature, "vana", "vana-"), 
  T ~ tolower(source_literature)
)) 

op_count <- op_count + count_diff_vec(before, data_eng$source_literature)

```

## `title`

```{r}
before <- data_eng$title

data_eng$title <- data_eng$title |>  str_replace(fixed("#D"), "")
data_eng$title <- data_eng$title|> str_replace(fixed("*"), "")
op_count <- op_count + count_diff_vec(before, data_eng$title)
before <- data_eng$title
data_eng <- data_eng|> mutate(title = case_when(
    title == "" ~ NA,
    T ~ title
  ))

op_count <- op_count + count_diff_vec(before, data_eng$title)
```

##  `author`

```{r}
before <- data_eng$author
data_eng <- data_eng|> mutate(
  author = case_when(
    author == "" | author == "π" | author == "teadmata" ~ NA,
    T ~ author
  ))
op_count <- op_count + count_diff_vec(before, data_eng$author)
```

## `title_original`

```{r}
before <- data_eng$title_original

data_eng <- data_eng|> mutate(title_original = case_when(
    title_original == "ˇteadmata" | title_original == "teadmata" ~ NA,
    T ~ title_original
  ))

op_count <- op_count + count_diff_vec(before, data_eng$title_original)
```

## `translator`

```{r}
before <- data_eng$translator

data_eng$translator <- data_eng$translator|> str_replace("<<mf>>", "") 
data_eng$translator <- data_eng$translator|> str_replace(fixed("|d"), " ")
data_eng <- data_eng |> mutate(translator = case_when(
    translator == "teadmata" | translator == "" ~ NA,
    T ~ translator
  ))

op_count <- op_count + count_diff_vec(before, data_eng$translator)
```

## `editor`

```{r}
before <- data_eng$editor

data_eng <- data_eng|> mutate(
  editor = case_when(
    editor == "" | editor == "teadmata" ~ NA,
    T ~ editor
  ))

op_count <- op_count + count_diff_vec(before, data_eng$editor)
```

## `fore_afterword_author`

```{r}
before <- data_eng$fore_afterword_author

data_eng$fore_afterword_author <- data_eng$fore_afterword_author |> str_replace(fixed("ˇˇ"), "")
data_eng <- data_eng|> mutate(fore_afterword_author = case_when(
    fore_afterword_author == "" | fore_afterword_author == "teadmata" ~ NA,
    T ~ fore_afterword_author
  ))

op_count <- op_count + count_diff_vec(before, data_eng$fore_afterword_author)
```

## `publication_location`

```{r}
before <- data_eng$publication_location

data_eng <- data_eng |> mutate(publication_location = case_when(
    publication_location == "" | publication_location == "teadmata" ~ NA,
    T ~ publication_location
  ))

op_count <- op_count + count_diff_vec(before, data_eng$publication_location)

```

## `publisher`

```{r}
before <- data_eng$publisher

data_eng <- data_eng |> mutate(publisher = case_when(
    publisher == "" | publisher == "teadmata" ~ NA,
    publisher == "A. Tõllasepp" ~ "A. Tõllasepp", 
    publisher == "Ajalehtede ja Ajakirjade Kirjastus" ~ "Ajalehtede-Ajakirjade Kirjastus",
    publisher == "Allika" ~ "Allika Kirjastus", 
    publisher == "AVIV" ~ "Aviv", 
    publisher == "Draakon ja Kuu" ~ "Draakon & Kuu", 
    publisher == "Draama Stuudio" ~ "Draamastuudio", 
    publisher == "Draamateaater" ~ "Draamateater", 
    publisher %in% c("E.B.K Selts","E.B. Kirjanduse Selts","EBK Selts") ~ "E.B.K. Selts",
    publisher == "ECOTALENT" ~ "Ecotalent", 
    publisher == "EELK Pühapäevakooliühendus" ~ "EELK Pühapäevakooli Ühendus",
    publisher == "Eesti Ekspress" ~ "Eesti Ekspressi Kirjastus" ,
    publisher %in% c("Eesti Draama Studio","Eesti Draama Stuudio") ~ 'Eesti Draamastuudio',
    publisher %in% c("Eesti Kirjanduse Seltsi koolikirjanduse-toimkond", 
                     "Eesti Kirjanduse Selts Koolikirjanduse toimkond", 
                     "Eesti Kirjanduse Seltsi koolikirjanduse toimkond") ~ "Eesti Kirjanduse Seltsi Koolikirjanduse toimkond", 
    publisher == "Eesti Kirjastuse Kooperatiiv," ~ "Eesti Kirjastuse Kooperatiiv", 
    publisher == "Eesti Päevalehe Kirjastus" ~ "Eesti Päevaleht", 
    publisher %in% c("Eesti Pimedate Ühingu Heli- ja Punktkirjakeskus",
                     "Eesti Pimedate Ühingu Heli-ja Punktkirja Keskus") ~ "Eesti Pimedate Ühingu Heli- ja Punktkirja Keskus", 
    publisher == "Eesti Raamat," ~ "Eesti Raamat", 
    publisher %in% c("Eestimaa Kooliõpetajate Vastastiku Abiandmise Selts", 
                     "Eestimaa Kooliõpetajate Vastastikkuse Abiandmise Selts") ~ "Eestimaa Kooliõpetajate Vastastikku Abiandmise Selts",
    publisher == "Eestimaa Kooliõpetajate Vastastiku Abiandmise Seltsi raamatukauplus" ~ "Eestimaa Kooliõpetajate Vastastikku Abiandmise Seltsi raamatukauplus", 
    publisher == "EKP KK Kirjastus" ~ "EKP Keskkomitee Kirjastus",
    publisher == "Kommunistlise partei Eestimaa keskkomitee"  ~ "EKP Keskkomitee Kirjastus",
    publisher == "EÜS Veljesto kirjastus" ~ "EÜS Veljesto Kirjastus",
    publisher == "Hendrik Lindepuu" ~ "Hendrik Lindepuu Kirjastus",
    publisher == 'Heliraamatute Kirjastusfond "Helikiri' ~ "Heliraamatute Kirjastusfond Helikiri", 
    publisher == "Hendrik Lindepuu" ~ "Hendrik Lindepuu Kirjastus",
    publisher == "Kristliku Rahvakirjanduse agentur" ~ "Kristliku rahvakirjanduse agentur",
    publisher == "Odamees-Carl Sarap" ~ "Odamees", 
    publisher == "Odamees/Carl Sarap" ~ "Odamees", 
    publisher == "Pilgrim Group" ~ "Pilgrim",
    publisher %in% c("Pimedate infoühing Helikiri", 
                     'Pimedate Infoühing "Helikiri') ~ "Pimedate Infoühing Helikiri", 
    publisher == "Saksala Kirjastusühisus" ~ "Sakala Kirjastusühisus", 
    publisher %in% c("T. Mutsu teatrikirjastus", 
                     "T. Mutsu Teatrikirjastus", 
                     "T. Mutsu Teaterkirjastus") ~ "T. Mutsu Theater Kirjastus", 
    publisher %in% c("Tallinna Eesti Kirjastuse-ühisus", 
                     "Tallinna Eesti Kirjastuse-Ühisus") ~ "Tallinna Eesti Kirjastus-Ühisus", 
    publisher %in% c("Tallinna Töölisteaater", 
                     "Tallinna Töölisteatri ühing", 
                     "Tallinna Töölisteatri Yhing") ~ "Tallinna Töölisteatri Ühing", 
    publisher == "TormiKiri" ~ "Tormikiri",
    publisher == "TRAVON"~ "Travon", 
    publisher == "Uuem kirjandus" ~ "Uuem Kirjandus", 
    publisher == "V. K. P. K.-K. Siberi Oblasti büroo Eesti sektsioon" ~ "V. K. P. KK Siberi Oblasti buroo Eesti sektsioon", 
    publisher == "Välismaatööliste kirjastusühisus NSV Liidus" ~ "Välismaatööliste Kirjastusühisus NSV Liidus",
    publisher == "Varak" ~ "Varrak", 
    publisher == "Viroonia" ~ "Vironia", 
    T ~ publisher
  ))
op_count <- op_count + count_diff_vec(before, data_eng$publisher)
```

## `physical_description`

```{r}
before <- data_eng$physical_description

data_eng$physical_description <- data_eng$physical_description |> str_replace(fixed("ˇ"), "")
data_eng <- data_eng |> mutate(physical_description = case_when(
    physical_description == "" ~ NA,
    T ~ physical_description
  ))
op_count <- op_count + count_diff_vec(before, data_eng$physical_description)
```

## `edition`

```{r}
before <- data_eng$edition

data_eng$edition <- data_eng$edition |> str_replace(fixed("ˇˇ"), "")
data_eng <- data_eng |> mutate(edition = case_when(
    edition == "ˇˇ" | edition == "" ~ NA,
    T ~ edition
  ))
op_count <- op_count + count_diff_vec(before, data_eng$edition)
```

## `series`

```{r}
before <- data_eng$series

data_eng <- data_eng |> mutate(series = case_when(
    series == "ˇˇ" | series == "" ~ NA,
    T ~ series
  ))
op_count <- op_count + count_diff_vec(before, data_eng$source_language)
```

## `author_of_translated_book_under_review_to_be_removed`

```{r}
before <- data_eng$author_of_translated_book_under_review_to_be_removed

data_eng$author_of_translated_book_under_review_to_be_removed <- 
  data_eng$author_of_translated_book_under_review_to_be_removed |> 
  str_replace("<p>", "") 
data_eng$author_of_translated_book_under_review_to_be_removed <-
  data_eng$author_of_translated_book_under_review_to_be_removed |> 
  str_replace("</p>", "")  
data_eng$author_of_translated_book_under_review_to_be_removed <-
  data_eng$author_of_translated_book_under_review_to_be_removed |> 
  str_replace(fixed("ˇˇ"), "")
data_eng$author_of_translated_book_under_review_to_be_removed <-
  data_eng$author_of_translated_book_under_review_to_be_removed |> 
  str_replace(fixed('<span style="font-weight: 400">'), "")
data_eng$author_of_translated_book_under_review_to_be_removed <-
  data_eng$author_of_translated_book_under_review_to_be_removed |> 
  str_replace(fixed('</span>'), "")

data_eng <- data_eng |> 
  mutate(author_of_translated_book_under_review_to_be_removed = case_when(
    author_of_translated_book_under_review_to_be_removed == "" | 
      author_of_translated_book_under_review_to_be_removed == "teadmata" ~ NA,
    T ~ author_of_translated_book_under_review_to_be_removed
  ))

op_count <- op_count + count_diff_vec(before, data_eng$source_language)
```

## `issue`

```{r}
op_count2 <- 0
before2 <- data_eng$author_of_translated_book_under_review_to_be_removed

data_eng$issue <- data_eng$issue |> str_replace("<p>", "") 
data_eng$issue <- data_eng$issue |> str_replace("</p>", "") 
data_eng$issue <- data_eng$issue |> str_replace('<span style="font-weight: 400">', '') 
data_eng$issue <- data_eng$issue |> str_replace('</span>', '')
data_eng <- data_eng |> mutate(
  issue = case_when(
    issue == "teadmata" |
    issue == "" ~ NA,
    T ~ issue
  ))

op_count2 <- op_count2 + count_diff_vec(before2, data_eng$source_language)

```

## `n_pages`

```{r}
data_eng$n_pages <- data_eng$n_pages |> str_replace(fixed("ˇ"), "")
data_eng <- data_eng |> mutate(
  n_pages = case_when(
    n_pages == "" ~ NA,
    T ~ n_pages
  ))
```

## `content`

```{r}

data_eng$content <- data_eng$content |> str_replace("<p>", "")
data_eng$content <- data_eng$content |> str_replace("</p>", "")
data_eng$content <- data_eng$content |> str_replace("&nbsp;", "") 
data_eng$content <- data_eng$content |> str_replace("<br />", " ")
data_eng <- data_eng |> mutate(
  content = case_when(
    content == "" ~ NA,
    T ~ content
  ))
```

## `notes` 

```{r}

data_eng$notes <- data_eng$notes |> str_replace(fixed("ˇ"), "") 
data_eng$notes <- data_eng$notes |> str_replace("<<mf>>", "")
data_eng$notes <- data_eng$notes |> str_replace(fixed("ˇ"), "") 
data_eng$notes <- data_eng$notes |> str_replace("<<mf>>", "")
data_eng <- data_eng |> mutate(
  notes = case_when(
    notes == "" ~ NA,
    T ~ notes
  ))
```

# duplicates removal 

```{r}
before2 <- data_eng
data_eng <- data_eng[!duplicated(data_eng),]
op_count2 <- op_count2 + count_diff_df(before2, data_eng)
```

# write processed data

```{r}
write.csv(data_eng, 'data/processed_translation_data_4.csv')
```


# Manual changes to be done 

- [ ] `publication_year` < 1850 -> strange values, one value 
- [ ] `max(data_eng$publication_year)` -> strange value 

