---
title: "data_processing_pipeline"
output: html_document
---

# Pipeline 

In this file functional pipeline: raw -> processed data 

```{r setup}
library(dplyr)
library(stringr)

data = read.csv("data/translation_data_possible_duplicates.csv")
new_names = read.csv('data/translated_names.csv')

data_eng <- data
colnames(data_eng) <- new_names$x
```


# translation of variable names 

```{r, eval=F}
# translated names 

translated_names <- c(
  'teaviku_laad'="publication_type",
  'sihtrühm'="target_audience", 
  'pealkiri'="title",
  'autor'="author",
  'originaal_pealkiri'="title_original",
  'Žanr'="genre",
  'tõlkija'="translator", 
  'lähtekeel'="source_language", 
  'lähtekirjandus'="source_literature",
  'toimetaja'="editor",
  'ees__järelsõna_autor'="fore_afterword_author",
  'ilmumiskoht'="publication_location",
  'kirjastaja'="publisher", 
  'ilmumisaasta'="publication_year", 
  'füüsiline_kirjeldus'="physical_description", 
  'trükikordus'="edition", 
  'sarjaandmed'="series", 
  'arvustatava_tõlkeraamatu_autor'="author_of_translated_book_under_review_to_be_removed", 
  'väljaanne'="issue", 
  'number_leheküljed'="n_pages", 
  'sisu'="content", 
  'märkused'="notes", 
  'id'="id") 

write.csv(translated_names, 'data/translated_names.csv')
```


# Standardisation of the variables 

1. standardise 
2. divide dataset into: one category X multiple categories in one var 
3. split the data points with multiple values in one categories into multiple rows
4. 


## publication_type 

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.

```{r}
data_eng <- data_eng |> mutate(publication_type = case_when(
  publication_type %in% c("", " ", "-")  ~ NA, 
  publication_type == "Tõlkeraamnat" ~ "Tõlkeraamat", 
  publication_type == "tõlkeraamat" ~ "Tõlkeraamat",
  T ~ publication_type 
)) 
```

## target_audience 

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.

```{r}
data_eng <- data_eng |> mutate(target_audience = case_when(
  target_audience %in% c(" ", "") ~ NA, 
  target_audience == "laste- ja noortekirjandus" ~ "Laste- ja noortekirjandus", 
  target_audience == "Täiskasvanute lukirjandus" ~ "Täiskasvanute ilukirjandus", 
  target_audience == "Laste ja noortekirjandus" ~ "Laste- ja noortekirjandus", 
  T ~ target_audience
))
```




## removing the multiples 

```{r}
data_to_be_split <- data_eng |> filter(str_detect(publication_type, ", "))
data_eng <- data_eng |> filter(!str_detect(publication_type, ", ") & 
                                 !str_detect(target_audience, ', '))
```

