---
title: "data_processing_pipeline"
output: html_document
---

# Pipeline 

In this file functional pipeline: raw -> processed data 

```{r setup}
library(dplyr)
library(stringr)

data = read.csv("data/translation_data_full_duplicates.csv")
new_names = read.csv('data/translated_names.csv')

data_eng <- data
colnames(data_eng) <- new_names$x
```


# translation of variable names 

```{r, eval=F}
# translated names 

translated_names <- c(
  'teaviku_laad'="publication_type",
  'sihtrühm'="target_audience", 
  'pealkiri'="title",
  'autor'="author",
  'originaal_pealkiri'="title_original",
  'Žanr'="genre",
  'tõlkija'="translator", 
  'lähtekeel'="source_language", 
  'lähtekirjandus'="source_literature",
  'toimetaja'="editor",
  'ees__järelsõna_autor'="fore_afterword_author",
  'ilmumiskoht'="publication_location",
  'kirjastaja'="publisher", 
  'ilmumisaasta'="publication_year", 
  'füüsiline_kirjeldus'="physical_description", 
  'trükikordus'="edition", 
  'sarjaandmed'="series", 
  'arvustatava_tõlkeraamatu_autor'="author_of_translated_book_under_review_to_be_removed", 
  'väljaanne'="issue", 
  'number_leheküljed'="n_pages", 
  'sisu'="content", 
  'märkused'="notes", 
  'id'="id") 

write.csv(translated_names, 'data/translated_names.csv')
```


# Standardisation of the variables 


1. split the data points with multiple values in one categories into multiple rows
2. standardise 
3. divide dataset into: one category X multiple categories in one var 
  - using the existing id I can then match the duplicates 
4. 


## publication_type 

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.

```{r}
data_eng <- data_eng |> mutate(publication_type = case_when(
  publication_type %in% c("", " ", "-")  ~ NA, 
  publication_type == "Tõlkeraamnat" ~ "Tõlkeraamat", 
  publication_type == "tõlkeraamat" ~ "Tõlkeraamat",
  T ~ publication_type 
)) 
```

## target_audience 

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.

```{r}
data_eng <- data_eng |> mutate(target_audience = case_when(
  target_audience %in% c(" ", "") ~ NA, 
  target_audience == "laste- ja noortekirjandus" ~ "Laste- ja noortekirjandus", 
  target_audience == "Täiskasvanute lukirjandus" ~ "Täiskasvanute ilukirjandus", 
  target_audience == "Laste ja noortekirjandus" ~ "Laste- ja noortekirjandus", 
  T ~ target_audience
))
```


## genre

Standardizing:
- split values from "; "
- empty values "" standardize to NULL
- put genres in all lowercase (after filtering out `Muzl, der gestiefelte Kater`)
- all values are in plural 

```{r}
data_eng <- data_eng |> mutate(genre = case_when(
  genre %in% c(" ", "", 'j') ~ NA, 
  genre == "romaanidq" ~ "romaanid",
  genre == "Muzl, der gestiefelte Kater" ~ NA, 
  genre == "romaan" ~ "romaanid", 
  genre == "rtomaanid" ~ "rommanid",
  genre == "dramatiseering" ~ "dramatiseeringud", 
  genre == "jutt" ~ "jutud", 
  genre == "jutus" ~ "jutud", 
  genre == "jutustus" ~ "jutustused", 
  genre == "jutustuse" ~ "jutustused", 
  genre == "jutustusedd" ~ "jutustused", 
  genre == "näidenid" ~ "näidendid", 
  T ~ tolower(genre)
))
```


# duplicates removal 
```{r}
data_eng <- data_eng[!duplicated(data_eng),] 
```

# write processed data

```{r}
write.csv(data_eng, 'data/processed_translation_data_1.csv')
```









## removing the multiples 

```{r}
data_to_be_split <- data_eng |> filter(str_detect(publication_type, ", "))
data_eng <- data_eng |> filter(!str_detect(publication_type, ", ") & 
                                 !str_detect(target_audience, ', '))
```

