---
title: "standardizing-values"
output: html_document
---

TODO: 
keep track of interventions and deletion 
reviews and translation - different? 
- [] go through this document and standardize
- [] split names: first name, last name

```{r}
data = read.csv("data/translation_data_possible_duplicates.csv")
new_names = read.csv('data/translated_names.csv')
data |> colnames()
data_eng <- data
colnames(data_eng) <- new_names$x
data_eng |> colnames()

data_to_be_split # rows of vars with more values 
```

# Standardizing the somewhat-fixed columns

All of them can have multiple values, by the way.

## Column "Teaviku laad" ()
All current values:
```
 [1] "Tõlkearvustus"                                     
 [2] "Perioodikas ilmunud tõlge"                         
 [3] "Kogumikus ilmunud tõlge"                           
 [4] "Tõlkeraamat"                                       
 [5] "Perioodikas ilmunud tõlge, Tõlkearvustus"          
 [6] ""                                                  
 [7] "Tõlkeraamnat"                                      
 [8] "-"                                                 
 [9] "Kogumikus ilmunud tõlge, Perioodikas ilmunud tõlge"
[10] "tõlkeraamat"                                       
```

Standardizing:
- split values from ", "
- empty values "" and "-" standardize to NULL
- names:
  - "Tõlkearvustus"
  - "Perioodikas ilmunud tõlge"
  - "Kogumikus ilmunud tõlge"
  - "Tõlkeraamat"
with the first letter capitalized.


```{r}
data_eng |> names()
data_eng |> select(publisher) |> filter(str_detect(publisher, 'ja ')) |> unique()
``` 


```{r}
data |> select(teaviku_laad) |> unique()
data_eng |> select(publication_type) |> unique()

data_eng$publication_type |> unique()

# data_eng |> mutate(publication_type = case_when(
#   (data_eng$publication_type == "" | data_eng$publication_type == "-") ~ NULL, 
#   T ~ publication_type))

data_eng <- data_eng |> mutate(publication_type = case_when(
  publication_type == "" | 
    publication_type == " " | 
    publication_type == "-"  ~ NA, 
  T ~ publication_type ))

data_to_be_split <- data_eng |> filter(publication_type == "-")
```


## Column "Sihtrühm" ()
All current values:
```
[1] "Täiskasvanute ilukirjandus"                           
[2] "Laste- ja noortekirjandus"                            
[3] ""                                                     
[4] "Laste- ja noortekirjandus, Täiskasvanute ilukirjandus"
[5] "Laste ja noortekirjandus"                             
[6] "Täiskasvanute iluirjandus"                            
[7] "laste- ja noortekirjandus"                            
[8] "Täiskasvanute lukirjandus"                            
```

Standardizing:
- split values from ", "
- empty values "" standardize to NULL
- names:
  - "Täiskasvanute ilukirjandus"
  - "Laste- ja noortekirjandus"
with the first letter capitalized.

```{r}

```



## Column "Žanr" ()
Standardizing:
- split values from "; "
- empty values "" standardize to NULL
- put genres in all lowercase (after filtering out `Muzl, der gestiefelte Kater`)


## Columns "lähtekeel" and "lähtekirjandus" ()
Standardizing:
- split values from "; "
- empty values "" standardize to NULL
- put genres in all lowercase (after filtering out `Muzl, der gestiefelte Kater`)


